---
title: "Clean Raw Data"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

librarian::shelf("freeR", "glue", "googledrive", "here", "janitor", "lubridate", "readxl", "tidyverse")

options(scipen=999)

dir_gdrive <- "/Volumes/GoogleDrive/Shared drives/Palmyra_DataTransfer_EDI_Project"
```

## Read in the Data from Google Drive 

To do this step, you need to have Google Drive installed on your computer so that you can access Google Drive files using Google File Stream 

### Colonies Data
```{r}
# Palmyra May 2011 Data 

colonies <- read_excel(glue("{dir_gdrive}/DATA_RAW/Greta Aeby/Palmyra may 2011.xlsx"), sheet = "tagged colonies" ) %>% clean_names()

colony_location <- read_excel(glue("{dir_gdrive}/DATA_RAW/Greta Aeby/Palmyra may 2011.xlsx"), sheet = "tag colony location" ) %>% clean_names()

crazy_coral_sites <- read_excel(glue("{dir_gdrive}/DATA_RAW/Greta Aeby/Palmyra may 2011.xlsx"), sheet = "crazycoral disease surveys site" ) %>% clean_names()

sites <- read_excel(glue("{dir_gdrive}/DATA_RAW/Greta Aeby/Palmyra may 2011.xlsx"), sheet = "sites" ) %>% clean_names()

tagged_colony_gps <- read_excel(glue("{dir_gdrive}/DATA_RAW/Greta Aeby/Palmyra may 2011.xlsx"), sheet = "tagged colony GPS" ) %>% clean_names()

```

#### Explore Colonies and Sites Data 

```{r}
str(colonies)
sort(unique(colonies$date_tagged))
sort(unique(colonies$sampled_for_histo))
sort(unique(colonies$neighboring_colony_affected_on_6_3_11))

str(sites)
sort(unique(sites$date))
sort(unique(sites$gps))

str(tagged_colony_gps)
sort(unique(tagged_colony_gps$long))


```

- Colonies 
  - `sampled_for_histo` is not reading in as Date, needs to be fixed 
  - Make `sampled_for_transmission` a Date 

- Colony Location looks good! 
- Crazy Coral Sites looks good! 

- Sites 
  - Split `GPS` into a lat and long coordinate column 
  
- Tagged Location GPS looks good! 


#### Clean the Data 

```{r}
colonies_clean <- colonies %>% 
  mutate(sampled_for_histo = case_when(
    sampled_for_histo == "40683.0" ~ "2011-05-20", 
    sampled_for_histo == "y" ~ "y"
  ))

sites_clean <- sites %>% 
  separate(gps, into = c("lat", "lon"), sep = "  ")

```




```{r}

transmission_samples <- read_excel(glue("{dir_gdrive}/DATA_RAW/Greta Aeby/Palmyra may 2011.xlsx"), sheet = "transmission samples" ) %>% clean_names()

substrate_surveys <- read_excel(glue("{dir_gdrive}/DATA_RAW/Greta Aeby/Palmyra may 2011.xlsx"), sheet = "corallimorph substrate surveys" ) %>% clean_names() 

corallimorph_patch_survey <- read_excel(glue("{dir_gdrive}/DATA_RAW/Greta Aeby/Palmyra may 2011.xlsx"), sheet = "corallimorph patch surveys" ) %>% clean_names()

treated_colonies <- read_excel(glue("{dir_gdrive}/DATA_RAW/Greta Aeby/Palmyra may 2011.xlsx"), sheet = "treated colonies" ) %>% clean_names()

acrop_colony_counts <- read_excel(glue("{dir_gdrive}/DATA_RAW/Greta Aeby/Palmyra may 2011.xlsx"), sheet = "acrop colony cnts" ) %>% clean_names()

crazy_coral_dis <- read_excel(glue("{dir_gdrive}/DATA_RAW/Greta Aeby/Palmyra may 2011.xlsx"), sheet = "crazy coral dis 25x2" ) %>% clean_names()

substrate_summary <- read_excel(glue("{dir_gdrive}/DATA_RAW/Greta Aeby/Palmyra may 2011.xlsx"), sheet = "crzy corals substrate summary" ) %>% clean_names()

fish_data <- read_excel(glue("{dir_gdrive}/DATA_RAW/Greta Aeby/Palmyra may 2011.xlsx"), sheet = "fish data" ) %>% clean_names()
```


## Explore the Data 

```{r}
str(transmission_samples)
sort(unique(transmission_samples$date_collected))
sort(unique(transmission_samples$date_terminated))
sort(unique(transmission_samples$result))

str(substrate_surveys)

str(corallimorph_patch_survey)
sort(unique(corallimorph_patch_survey$number_corallimorph_patches))

str(treated_colonies)
sort(unique(treated_colonies$date_treated))
sort(unique(treated_colonies$treatment_type))
sort(unique(treated_colonies$notes))

str(acrop_colony_counts)
sort(unique(acrop_colony_counts$totals))

str(crazy_coral_dis)
sort(unique(crazy_coral_dis$description))

str(substrate_summary)

str(fish_data)

```

#### Changes

- Substrate Surveys
  - Should we make this long??
  
- Corallimorph Patch survey looks good!

- Treated Colonies 
  - Standardize the branch trim + zspar 
  - remove result 

- Acrop Colony Counts looks good! 
- Crazy Coral Dis looks good! 
- Substrate Summary Looks good! 
- Fish data looks good! 
  - Should it be long?


## Clean the Data 

```{r}

treated_colonies_clean <- treated_colonies %>% 
  select(-result)
treated_colonies_clean$treatment_type <- str_replace_all(treated_colonies$treatment_type, "branchlet trim and zspar", "zspar + branch trim")

sort(unique(treated_colonies_clean$treatment_type))

```

## Save the Clean Data 

Use this code chunk to upload the cleaned data directly to google drive. You write the file directly to the drive as if you were saving it to a local file 

```{r}
# You can use write_csv or any other function like that to write directly to the drive. 

# Example below: 
# write_csv(chlorurus_activity, glue("{dir_gdrive}/DATA_RAW/Peter 
# Carlson/Chlorurus_Activity_Palmyra_2014-test.csv"))



```



